\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-04-21 paper/main.tex
Fixed table 1, fixed author name, removed page number
small changes

\author{M. M. Abid Naziri}
\affiliation{%
  \institution{NC State University, USA}
  %\city{Rocquencourt}
  \country{}
}
\email{mnaziri@ncsu.edu}

@@

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
%% add page numbers
\pagestyle{plain}

@@

\begin{table}
  \centering
  \caption{\label{table:bug-characterization}Characterization of
    reproducible bugs from \tname.}
  %%   \Fix{Is this up to date? I have seen
  %% lots of activity recently but these numbers remain the
  %% same - Fixed (Abid)}\Fix{Can we add info about whether Python and/or C code causes
  %%     the bug? - Abid: we report how many c,python and cuda native files are buggy in total but not per bug, so currently no}\Fix{Can we add info on whether it is GPU related
  %%     (i.e., only manifests in GPUs)? - Abid: venv-docker is the same
  %%     as cpu-gpu}}
\begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 46 & 45-1 & 45-1 \\ \torch{} & 37 &
  18-19 & 21-16 \\ \tf{} & 24 & 23-1 & 24-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 86-21& 90-17
  \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
  \centering
  \caption{\label{table:bug-stats}Different bug manifestation types
    from \tname.}
  \begin{tabular}{lrrrrr}\toprule
    Bug manifestation type &Jax &Pytorch &Tensorflow &Total \\\midrule
    Incorrect Output &14 &11 &5 &30 \\
    Internal Exception &11 &9 &4 &24 \\
    Value Error &7 &0 &4 &11 \\
    Type Error &0 &1 &8 &9 \\
    Attribute Error &3 &2 &3 &8 \\
    Index Error &0 &7 &1 &8 \\
    Runtime Error &2 &0 &2 &4 \\
    Memory Error &2 &1 &0 &3 \\
    Invalid Argument Error &0 &2 &1 &3 \\
    Floating Point Error &1 &1 &0 &2 \\
    Error Not Raised &1 &0 &1 &2 \\
    Parse Error &0 &2 &0 &2 \\
    Runtime Warning &1 &0 &0 &1 \\
    Not Implemented Error &1 &0 &0 &1 \\
    Assertion Error &1 &0 &0 &1 \\
    Segmentation Fault &1 &0 &0 &1 \\
    Floating Point Exception &1 &0 &0 &1 \\
    Aborted &0 &1 &0 &1 \\
    \midrule
    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} &\numbugs{} \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}
  \centering
  \caption{\label{table:bug-interface}\tname's bug interface.}
\begin{tabular}{lp{6.5cm}}
  \toprule
  \textbf{command} & \textbf{description} \\
  \midrule
list-tests & List the tests available on this dataset\\
run-test & Runs one test\\
run-tests & Runs all the tests\\
run-tool & Runs a testing tool in a given buggy environment \\
show-info & Shows information about the tests available on this benchmark\\
stats & Shows statistics about this dataset (e.g., number of tests
that require GPU, number of tests that reproduce bugs in C or Python
code, etc.)\\
\bottomrule
\end{tabular}
\end{table}

@@

Let us use the bug 120903~\cite{torch120903} from \torch\ to demonstrate the
command \CodeIn{run-test}, which runs a test to reproduce a bug on an
environment with the necessary dependencies installed. Use the
following command to reproduce the bug:

@@

A developer needs to provide three scripts to integrate a fuzzing
tool: (1) a script that contains commands to run the tool (e.g. \CodeIn{run\_freefuzz\_docker.sh}); (2) a
preprocessing script to extract error types and buggy APIs for a
specific library version (\CodeIn{preprocess.py}), and (3) a postprocessing script to match the
execution log with the expected errors (\CodeIn{postprocess.py}) needs to be provided.
% \Fix{name
%   these scripts here and refer back to them in the text below} 
The
directory \CodeIn{tool-integration} that contains templates for these
scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
popular API fuzzer for DL libraries.
% \Fix{remove this paragraph. Explain the steps when they appear. It is difficult
%   to follow}
% \Fix{up to here}

We demonstrate the integration of FreeFuzz~\cite{wei2022free}. The
following script creates a Docker container associated with FreeFuzz.

@@

\section{Conclusion and Future Work}
Deep Learning (DL) Libraries (e.g., \torch) provide the basic blocks
for creating AI-enabled applications, which are becoming very
popular. Several testing techniques have been proposed in the
literature to find bugs in these libraries. Unfortunately, the lack of
a dataset of reproducible bugs in those libraries poses an important
barrier to the proper evaluation of these techniques. \tname{} fills
this gap. It includes a total of \numbugs\ across three major DL
libraries and provides an infrastructure to integrate fuzzers and
evaluate them. We plan to continue expanding this dataset and to
explore automated approaches to extract patches from issue trackers
and ``frontport'' them~\cite{hazimeh2020magma} to a single version of
the library to facilitate testing even further.

\section{Acknowledgements}
This work was supported and funded by the National Science Foundation grant numbers CCF-2349961.

>>>>

\author{M M Abid Naziri}
\affiliation{%
  \institution{NC State University, USA}
  %\city{Rocquencourt}
  \country{}
}
\email{mnaziri@ncsu.edu}

@@

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
%% add page numbers
% \pagestyle{plain}

@@

\begin{table}
  \centering
  \small
  \caption{\label{table:bug-characterization}Characterization of
    bugs from \tname.}
  \vspace{-1ex}
  %%   \Fix{Is this up to date? I have seen
  %% lots of activity recently but these numbers remain the
  %% same - Fixed (Abid)}\Fix{Can we add info about whether Python and/or C code causes
  %%     the bug? - Abid: we report how many c,python and cuda native files are buggy in total but not per bug, so currently no}\Fix{Can we add info on whether it is GPU related
  %%     (i.e., only manifests in GPUs)? - Abid: venv-docker is the same
  %%     as cpu-gpu}}
  \begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 46 & 45-1 & 45-1 \\ \torch{} & 37 &
  18-19 & 21-16 \\ \tf{} & 29 & 27-2 & 29-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 90-22& 95-17
  \\ \bottomrule
  \end{tabular}
  \vspace{-2ex}  
\end{table}

@@

\begin{table}
  \small
  \centering
  \caption{\label{table:bug-stats}Different bug manifestation types
    from \tname.}
  \vspace{-1ex}
  \begin{tabular}{lrrrrr}\toprule
    Bug manifestation type &Jax &Pytorch &Tensorflow &Total \\\midrule
    Incorrect Output &14 &11 &5 &30 \\
    Internal Exception &11 &9 &4 &24 \\
    Value Error &7 &0 &4 &11 \\
    Type Error &0 &1 &8 &9 \\
    Attribute Error &3 &2 &3 &8 \\
    Index Error &0 &7 &1 &8 \\
    Runtime Error &2 &0 &2 &4 \\
    Memory Error &2 &1 &0 &3 \\
    Invalid Argument Error &0 &2 &1 &3 \\
    Floating Point Error &1 &1 &0 &2 \\
    Error Not Raised &1 &0 &1 &2 \\
    Parse Error &0 &2 &0 &2 \\
    Runtime Warning &1 &0 &0 &1 \\
    Not Implemented Error &1 &0 &0 &1 \\
    Assertion Error &1 &0 &0 &1 \\
    Segmentation Fault &1 &0 &0 &1 \\
    Floating Point Exception &1 &0 &0 &1 \\
    Aborted &0 &1 &0 &1 \\
    \midrule
    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} &\numbugs{} \\
    \bottomrule
  \end{tabular}
  \vspace{-2ex}  
\end{table}

@@

\begin{table}
  \small
  \centering
  \caption{\label{table:bug-interface}\tname command-line interface.}
  \vspace{-1ex}
\begin{tabular}{lp{6.5cm}}
  \toprule
  \textbf{command} & \textbf{description} \\
  \midrule
list-tests & List the tests available on this dataset\\
run-test & Runs one test\\
run-tests & Runs all the tests\\
run-tool & Runs a testing tool in a given buggy environment \\
show-info & Shows information about the tests available on this benchmark\\
stats & Shows statistics about this dataset (e.g., number of tests
that require GPU, number of tests that reproduce bugs in C or Python
code, etc.)\\
\bottomrule
\end{tabular}
  \vspace{-3ex}
\end{table}

@@

Let us use bug 120903~\cite{torch120903} from \torch\ to demonstrate the
command \CodeIn{run-test}, which runs a test to reproduce a bug on an
environment with needed dependencies installed. Use the
following command to reproduce the bug:

@@

A developer needs to provide three scripts to integrate a fuzzing
tool: (1) a script that contains commands to run the tool (e.g. \CodeIn{run\_freefuzz\_docker.sh}); (2) a
preprocessing script to extract error types and buggy APIs for a
specific library version (\CodeIn{preprocess.py}), and (3) a postprocessing script to match the
execution log with the expected errors (\CodeIn{postprocess.py}) needs to be provided.
% \Fix{name
%   these scripts here and refer back to them in the text below} 
The
directory \CodeIn{tool-integration} contains templates for these
scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
popular API fuzzer for DL libraries.
% \Fix{remove this paragraph. Explain the steps when they appear. It is difficult
%   to follow}
% \Fix{up to here}
We demonstrate the integration of FreeFuzz~\cite{wei2022free}. The
following script creates a Docker container for FreeFuzz.

@@

\section{Conclusion and Future Work}
Deep Learning Libraries provide the basic blocks for creating
AI-enabled applications. Several testing techniques have been proposed
in the literature to find bugs in these libraries. Unfortunately, the
lack of a dataset of reproducible bugs in those libraries poses an
important barrier to the proper evaluation of these
techniques. \tname{} fills this gap. It includes a total of
\numbugs\ bugs across three major DL libraries and provides an
infrastructure to evaluate fuzzers.  To facilitate evaluation of
testing techniques even further we plan to continue expanding this
dataset and to explore automated approaches to ``frontport'' bugs into
single version of the library as in the Magma
benchmark~\cite{hazimeh2020magma}.

\section*{Acknowledgements}
This work was supported and funded by the National Science Foundation grant numbers CCF-2349961.
